AbxD01 Analysis

### 2015-02-26 abxD01_analysis.Rmd
Re-render markdown

### Figure 1: Bargraph
This figure was built using the R script called "stacked.barcharts.r", which contains the stackedbarcharts() funciton in the abxD01 folder.The input files are listed in Github. The graph can be sorted 2 ways either by the untreated's decreasing relabund (sortbyphyl=FALSE), or by the most abundant within each phylum (sortbyphyl=TRUE). For each treatment, the resulting *C. difficile* CFU/g Feces is also labeled on the Y axis below the treatment name. 
The parameters I changed in the r script were:
```{r, eval=TRUE}
abx<-c("Untreated", "Ciprofloxacin", "Clindamycin", "Vancomycin", "Streptomycin", "Cefoperazone", "Ampicillin", "Metronidazole")

# Generate the 
stackedbarcharts(file="~/Documents/Github/abxD01/Figure 1/abxD01.final.tx.2.subsample.relabund.topdose2.forlogscale.csv", fileIDS = "~/Documents/Github/abxD01/Figure 1/topdose_tx2_barchart_ids.csv", graphLabels = abx, sortbyphyl = TRUE, graphbyphyl = FALSE)

@@

@@

Statistical comparison of delayed and on time CFU results:
```{r, eval=TRUE}
file<-read.csv("~/Documents/Github/abxD01/Figure 5/abxD01.final.tx.2.subsample.allmetro.forlogscale.fig5.csv", header=T)
file<-file[file$expgroup!="1untr",]
avgCD<-tapply(file$nextDayCFU, file$expgroup, mean)
metro_avgCD<-format(avgCD, scientific=TRUE, digits=2)
file$nextDayCFU <- log10(file$nextDayCFU+1)
#kruskal.test(file$nextDayCFU ~ file$expgroup)
# p < 0.0001
#strep_CFU_wilcox <- pairwise.wilcox.test(file$nextDayCFU, file$expgroup, p.adj="BH")
# all significantly different
metro.aov<-aov(file$nextDayCFU ~ file$expgroup)
anova(metro.aov)
#TukeyHSD(strep.aov)
metro_ttest <- t.test(file$nextDayCFU~file$expgroup)
print(metro_ttest)
# both significantly different
```

>>>>

### Figure 1: Bargraph
This figure was built using the R script called "stacked.barcharts.r", which contains the stackedbarcharts() funciton in the abxD01 folder.The input files are listed in Github. The graph can be sorted 2 ways either by the untreated's decreasing relabund (sortbyphyl=FALSE), or by the most abundant within each phylum (sortbyphyl=TRUE). For each treatment, the resulting *C. difficile* CFU/g Feces is also labeled on the Y axis below the treatment name. 
The parameters I changed in the r script were:
```{r, eval=FALSE}
abx<-c("Untreated", "Ciprofloxacin", "Clindamycin", "Vancomycin", "Streptomycin", "Cefoperazone", "Ampicillin", "Metronidazole")
library(plotrix)
# Generate the 
stackedbarcharts(file="~/Documents/Github/abxD01/Figure 1/abxD01.final.tx.2.subsample.relabund.topdose2.forlogscale.csv", fileIDS = "~/Documents/Github/abxD01/Figure 1/topdose_tx2_barchart_ids.csv", graphLabels = abx, sortbyphyl = TRUE, graphbyphyl = FALSE)

@@

```{r, eval=FALSE}

@@

Statistical comparison of delayed and on time CFU results:
```{r, eval=TRUE}
file<-read.csv("~/Documents/Github/abxD01/Figure 5/abxD01.final.tx2.subsample.alldelay.relabund.csv", header=T)
file<-file[file$expgroup!="1untr",]
file$nextDayCFU <- log10(file$nextDayCFU+1)

metro <- file[file$abx=="Metronidazole", 3:4]
amp <- file[file$abx=="Ampicillin", 3:4]

diffs <- function(data){
  data.aov<-aov(data$nextDayCFU ~ data$expgroup)
  print(anova(data.aov))
  pairwise.t.test(data$nextDayCFU, data$expgroup, p.adjust="BH")
}

diffs(metro)
diffs(amp)
